---
title: "Flexdashboard with opencpu back-end"
output: 
  flexdashboard::flex_dashboard:
    theme: cerulean
    orientation: rows
    logo: testlogo.png
    social: [ "twitter", "facebook"]
    navbar:
      - { title: "About", href: "http://data-laborer.eu", align: right }
    source_code: "https://github.com/YvesCR/flexocpu"
---

```{r, echo=FALSE}
htmltools::tags$script(src = "//code.jquery.com/jquery-1.11.1.min.js")
htmltools::tags$script(src = "//cdn.opencpu.org/opencpu-0.4.js")
```

<script> 

$(function(){

$('#dashboard-container').css({'visibility': 'visible'}); 

  var paramid = 1;

  $('#myBtn').click( function () {
    
    $('#myBtn').hide();
    $('iframe').css({'display': 'inline'}); 
    
    var req2 = ocpu.call("make_map", {
        title : 'Chez Mamie:\n Best canteen of London'
      }, function(session){
        $('iframe').attr('src', session.getFileURL('mymap.html'));
      });
  });

  var jsonReqtime = ocpu.call("gethowel",{
      		id : Number(paramid)
      	}, function(session){
      	
      	session.getObject(function(outtxt){
      		$("#json_output").text(outtxt);
      		
      		var age_json = outtxt[0]["age"];
      		$('#age .value').text(age_json);
      		 if (age_json <= 21) {var color_age = '#01bb69';
      		  } else if (age_json <= 60) {var color_age = '#ff8039';
      	      } else {var color_age = '#fb305a';}
      		$('#age').css("background-color", color_age);
      		
      		var height_json = outtxt[0]["height"];
      		$('#height .value').text(height_json);
      		 if (height_json <= 140) {var color_income = '#ff8039';
      		  } else if (height_json >= 160) {var color_income = '#fb305a';
      	      } else {var color_income = '#01bb69';}
      		$('#height').css("background-color", color_income);
      		
      		var weight_json = outtxt[0]["weight"];
      		$('#weight .value').text(weight_json);
      		 if (weight_json <= 20) {var color_asset = '#ff8039';
      		  } else if (weight_json <= 40) {var color_asset = '#fb305a';
      	      } else {var color_asset = '#01bb69';}
      		$('#weight').css("background-color", color_asset);
      		
      		$('#id .value').text(outtxt[0]["id"]);
      		
      		var male_json = outtxt[0]["male"];
      		$('#sex .value').text(male_json);
      			 if (male_json === 0) {var color_male = '#ae6df8';
      		  } else {var color_male = '#02a8ee';}
      		$('#sex').css("background-color", color_male);
      		
      	});
  });
  
  var req = $("#plotdiv").rplot("plotind", {id : Number(paramid)});

});

$(function(){
  $("#idsubmit").click(function(e){
  
  var paramid = $("#myid").val();
  
  var jsonReqtime = ocpu.call("gethowel",{
    		id : Number(paramid)
    	}, function(session){
    	
    	session.getObject(function(outtxt){
    		$("#json_output").text(outtxt);
    		
      		var age_json = outtxt[0]["age"];
      		$('#age .value').text(age_json);
      		 if (age_json <= 21) {var color_age = '#01bb69';
      		  } else if (age_json <= 60) {var color_age = '#ff8039';
      	      } else {var color_age = '#fb305a';}
      		$('#age').css("background-color", color_age);
      		
      		var height_json = outtxt[0]["height"];
      		$('#height .value').text(height_json);
      		 if (height_json <= 140) {var color_income = '#ff8039';
      		  } else if (height_json >= 160) {var color_income = '#fb305a';
      	      } else {var color_income = '#01bb69';}
      		$('#height').css("background-color", color_income);
      		
      		var weight_json = outtxt[0]["weight"];
      		$('#weight .value').text(weight_json);
      		 if (weight_json <= 20) {var color_asset = '#ff8039';
      		  } else if (weight_json <= 40) {var color_asset = '#fb305a';
      	      } else {var color_asset = '#01bb69';}
      		$('#weight').css("background-color", color_asset);
      		
      		$('#id .value').text(outtxt[0]["id"]);
      		
      		var male_json = outtxt[0]["male"];
      		$('#sex .value').text(male_json);
      			 if (male_json === 0) {var color_male = '#ae6df8';
      		  } else {var color_male = '#02a8ee';}
      		$('#sex').css("background-color", color_male);
      		    		
    	});
    });
    
    var req = $("#plotdiv").rplot("plotind", {id : Number(paramid)});

  });

});
  
</script>

```{r setup, include=FALSE}
# devtools::install_github("Rstudio/flexdashboard")
library(flexdashboard)
```

Page 1
===================================== 

Row {data-height=200}
-------------------------------------

### Definition {data-width=800}

Test for a dashboard with opencpu.

Loading a page is slow due to the size of the web page loaded: so far 1.4 Mb.
Most of the size is due to the flexdashboard interface (multiple pages & tab adjustment).

There is a trade off between the complexity of the page (mobile compatible or not, multiple pages, etc.) and the size of the page.

### Selection (integer between 1 and 544) {data-width=200}

```{r}
htmltools::tags$input(type="integer", class="form-control", id="myid", value="1", style = "width: 90%")

htmltools::tags$button("Update dashboard!", type="submit", id="idsubmit", class="btn btn-default")
```

Row {data-height=200}
-----------------------------------------------------------------------

### Age

```{r valuebox1}
valueBox(0, icon = "fa-pencil", color = '#01bb69')
```

### Height

```{r valuebox2}
valueBox(0, icon = "fa-envelope-o", color = '#ff8039')
```

### Weight

```{r valuebox3}
valueBox(0, icon = "fa-trash", color = '#fb305a')
```

### Id

```{r}
valueBox(0, icon = "fa-puzzle-piece")
```

### Sex

```{r}
valueBox(0, icon = "fa-money", color = '#02a8ee')
```

Row {data-height=200}
-----------------------------------------------------------------------

### Indicator 1

```{r}
gauge(90, min = 0, max = 100, gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Indicator 2

```{r}
gauge(30, min = 0, max = 100, gaugeSectors(
  success = c(41, 50), warning = c(21, 40), danger = c(0, 20)
))
```

### Indicator 3

```{r}
gauge(8, min = 0, max = 100, gaugeSectors(
  success = c(0, 2), warning = c(3, 6), danger = c(7, 10)
))
```

Row {data-height=400}
-----------------------------------------------------------------------

### Age, Weight and Height Graphs

```{r}
htmltools::tags$div(id="plotdiv", style="height: 270px")
```

Page 2
===================================== 

Row {data-height=300}
-----------------------------------------------------------------------

### Age Height by Sex

```{r, fig.width=15}
data("howell")

ggplot2::ggplot(data = howell, ggplot2::aes(x = age, y = height, color = as.factor(male))) +
  ggplot2::geom_point()
```

### Age Weight by Sex

```{r, fig.width=15}
data("howell")

ggplot2::ggplot(data = howell, ggplot2::aes(x = age, y = weight, color = as.factor(male))) +
  ggplot2::geom_point()
```

Row {data-height=700}
-----------------------------------------------------------------------

### Mapping

```{r}

htmltools::tags$button("Map", type="button", id="myBtn")
htmltools::tags$iframe(src="about:blank", style='height: 620px;width: 1300px;display: none;')

```
